Demo arXiv template

### 2022-12-02 paper/paper.qmd
rearrange spatial processing

where $\psi \in \Psi \subseteq \mathbb{R}^{d_{\psi}}$ is the parameters associated with the temporal operation and $d_{\psi}$ is the number of parameter of $\psi$. 
A typical example of temporal processing is aggregation in the drought index SPI to measure the lack of precipitation for meteorological drought.
In SPI, monthly precipitation is aggregated by a time scale parameter $k$: $x(s_i;t_{j^\prime}) = \sum_{j = j^\prime-k+1}^{j^\prime}x(s_i; t_j),$ where $j^\prime$ is the new time index after the aggregation. In this notation, each spatial location is separately aggregated and precipitation is ummed from $k$ month back, $j^\prime - k + 1$, to the current period, $j^\prime$, to create the aggregated series, indexed by $j^\prime$.

*more explicit on k will influence 1) long term vs. short term, 2) uncertainty*
The choice of time scales parameter $k$ can result in variation in the calculated index values: a small $k$ of 3 or 6 months produces the index more sensitive to individual months, while a large $k$ of 24 or 36, an equivalent to a 2- or 3-year aggregation, gives dryness information relative to the long term condition. As will be shown in section [SECTION EXAMPLE], this variation may even lead to conflicting conclusions on the dry/wet condition of the area, highlighting the importance to account for index uncertainty when interpreting index values for decision-making.

@@

While many indexes are calculated independently on spatial locations, borrowing spatial information can happen at unobservable locations. Also, variables can be collected in different formats: some from satellite imageries as raster data, potentially at different resolutions, and some from ground stations as vector data. These spatial data need to be merged into a uniform unit to construct indexes. 
In the pipeline, spatial aggregation includes operations on the spatial dimension of the data and can be written as

\begin{equation}
g_{\mathcal{\theta}}(x(\mathbf{s};\mathbf{t})),
\end{equation}

where $\theta \in \Theta \subseteq \mathbb{R}^{d_{\theta}}$ is the spatial operation parameters and $d_{\theta}$ is the number of parameter of $\theta$. 
When one of the variables collected is only available in a coarser resolution, $i^\prime$, analysts may choose to reduce other variables with finer resolution, $i$, to match the coarser resolution. This is a spatial aggregation step and aggregating using the mean can be written as: $x(s_{i^\prime};t_{j}) = \bar{x}(s_{i \in i^\prime}; t_j),$, where $i \in i^\prime$ includes all the cells from the finer resolution in the coarser grid.

>>>>

where $\psi \in \Psi \subseteq \mathbb{R}^{d_{\psi}}$ is the parameters associated with the temporal operation and $d_{\psi}$ is the number of parameter of $\psi$. 
A typical example of temporal processing is aggregation, which is used in the drought index SPI to measure the lack of precipitation for meteorological drought.
In SPI, monthly precipitation is aggregated by a time scale parameter $k$: $x(s_i;t_{j^\prime}) = \sum_{j = j^\prime-k+1}^{j^\prime}x(s_i; t_j),$ where $j^\prime$ is the new time index after the aggregation. In this notation, each spatial location is separately aggregated and precipitation is summed from $k$ month back, $j^\prime - k + 1$, to the current period, $j^\prime$, to create the aggregated series, indexed by $j^\prime$.

*more explicit on k will influence 1) long term vs. short term, 2) uncertainty*

The choice of time scales parameter $k$ can result in variation in the calculated index values: a small $k$ of 3 or 6 months produces the index more sensitive to individual months, while a large $k$ of 24 or 36, an equivalent to a 2- or 3-year aggregation, gives dryness information relative to the long term condition. As will be shown in section [SECTION EXAMPLE], this variation may even lead to conflicting conclusions on the dry/wet condition of the area, highlighting the importance to account for index uncertainty when interpreting index values for decision-making.

@@

Spatial processing may be needed when indexes are not calculated independently on each collected location or when variables collected from multiple sources need to be fused before further processing. The process can be written as a general operation in the form of

\begin{equation}
x(\mathbf{s}^\prime;\mathbf{t}) = g_{\mathcal{\theta}}(x(\mathbf{s};\mathbf{t})),
\end{equation}

where $\theta \in \Theta \subseteq \mathbb{R}^{d_{\theta}}$ is the associated parameters in the process and $d_{\theta}$ is the number of parameter of $\theta$. 
An example of spatial processing is to align variables collected in different resolutions.
When variables are collected at different resolutions, analysts may choose to down-sample those in a finer resolution, $i$, to match those in a coarser resolution, $i^\prime$. This is a spatial aggregation and if aggregate using the mean, it can be written as

\begin{equation}
g(x) = \frac{\sum_{i \in i^\prime}x}{n_{i^\prime}},
\end{equation}

where $i \in i^\prime$ includes all the cells from the finer resolution in the coarser grid and $n_{i^\prime}$ is the number of observations falls into the  coarser grid. Other examples of spatial processing include 1) borrowing information from neighbouring spatial locations to interpolate unobserved locations and 2) fusing variables from ground measures with satellite imageries.

### 2022-12-02 paper/paper.tex
rearrange spatial processing

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, interior hidden]}{\end{tcolorbox}}\fi

@@

An overview of the pipeline is given in Figure~\ref{fig-pipeline-steps}
to illustrate the construction from raw data to the final indexes. The
pipeline includes modules for operations in the spatial, temporal, and
multivariate aspects of the data as well as modules for comparing and
communicating indexes (benchmarking and simplification). Analysts are
free to select the modules they need and arrange them in the order they
see fit to construct indexes. While the starting point of the pipeline
is raw data, there are steps prior to this that are crucial to the
success of an index. For example, the defined index needs to be useful
for measuring the concept of interest and variables need to be collected
from reliable sources with proper quality control.

@@

where \(\psi \in \Psi \subseteq \mathbb{R}^{d_{\psi}}\) is the
parameters associated with the temporal operation and \(d_{\psi}\) is
the number of parameter of \(\psi\). A typical example of temporal
processing is aggregation in the drought index SPI to measure the lack
of precipitation for meteorological drought. In SPI, monthly
precipitation is aggregated by a time scale parameter \(k\):
\(x(s_i;t_{j^\prime}) = \sum_{j = j^\prime-k+1}^{j^\prime}x(s_i; t_j),\)
where \(j^\prime\) is the new time index after the aggregation. In this
notation, each spatial location is separately aggregated and
precipitation is ummed from \(k\) month back, \(j^\prime - k + 1\), to
the current period, \(j^\prime\), to create the aggregated series,
indexed by \(j^\prime\).

\emph{more explicit on k will influence 1) long term vs.~short term, 2)
uncertainty} The choice of time scales parameter \(k\) can result in
variation in the calculated index values: a small \(k\) of 3 or 6 months
produces the index more sensitive to individual months, while a large
\(k\) of 24 or 36, an equivalent to a 2- or 3-year aggregation, gives
dryness information relative to the long term condition. As will be
shown in section {[}SECTION EXAMPLE{]}, this variation may even lead to
conflicting conclusions on the dry/wet condition of the area,
highlighting the importance to account for index uncertainty when
interpreting index values for decision-making.

@@

While many indexes are calculated independently on spatial locations,
borrowing spatial information can happen at unobservable locations.
Also, variables can be collected in different formats: some from
satellite imageries as raster data, potentially at different
resolutions, and some from ground stations as vector data. These spatial
data need to be merged into a uniform unit to construct indexes. In the
pipeline, spatial aggregation includes operations on the spatial
dimension of the data and can be written as

\begin{equation}
g_{\mathcal{\theta}}(x(\mathbf{s};\mathbf{t})),
\end{equation}

where \(\theta \in \Theta \subseteq \mathbb{R}^{d_{\theta}}\) is the
spatial operation parameters and \(d_{\theta}\) is the number of
parameter of \(\theta\). When one of the variables collected is only
available in a coarser resolution, \(i^\prime\), analysts may choose to
reduce other variables with finer resolution, \(i\), to match the
coarser resolution. This is a spatial aggregation step and aggregating
using the mean can be written as:
\(x(s_{i^\prime};t_{j}) = \bar{x}(s_{i \in i^\prime}; t_j),\), where
\(i \in i^\prime\) includes all the cells from the finer resolution in
the coarser grid.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, frame hidden, breakable, sharp corners, interior hidden]}{\end{tcolorbox}}\fi

@@

An overview of the pipeline is given in Figure~\ref{fig-pipeline-steps}
to illustrate the construction from raw data to the final indexes. The
pipeline includes modules for operations in the spatial, temporal, and
multivariate aspects of the data as well as modules for comparing and
communicating indexes. Analysts are free to select the modules they need
and arrange them in the order they see fit to construct indexes. While
the starting point of the pipeline is raw data, there are steps prior to
this that are crucial to the success of an index. For example, the
defined index needs to be useful for measuring the concept of interest
and variables need to be collected from reliable sources with proper
quality control.

@@

where \(\psi \in \Psi \subseteq \mathbb{R}^{d_{\psi}}\) is the
parameters associated with the temporal operation and \(d_{\psi}\) is
the number of parameter of \(\psi\). A typical example of temporal
processing is aggregation, which is used in the drought index SPI to
measure the lack of precipitation for meteorological drought. In SPI,
monthly precipitation is aggregated by a time scale parameter \(k\):
\(x(s_i;t_{j^\prime}) = \sum_{j = j^\prime-k+1}^{j^\prime}x(s_i; t_j),\)
where \(j^\prime\) is the new time index after the aggregation. In this
notation, each spatial location is separately aggregated and
precipitation is summed from \(k\) month back, \(j^\prime - k + 1\), to
the current period, \(j^\prime\), to create the aggregated series,
indexed by \(j^\prime\).

\emph{more explicit on k will influence 1) long term vs.~short term, 2)
uncertainty}

The choice of time scales parameter \(k\) can result in variation in the
calculated index values: a small \(k\) of 3 or 6 months produces the
index more sensitive to individual months, while a large \(k\) of 24 or
36, an equivalent to a 2- or 3-year aggregation, gives dryness
information relative to the long term condition. As will be shown in
section {[}SECTION EXAMPLE{]}, this variation may even lead to
conflicting conclusions on the dry/wet condition of the area,
highlighting the importance to account for index uncertainty when
interpreting index values for decision-making.

@@

Spatial processing may be needed when indexes are not calculated
independently on each collected location or when variables collected
from multiple sources need to be fused before further processing. The
process can be written as a general operation in the form of

\begin{equation}
x(\mathbf{s}^\prime;\mathbf{t}) = g_{\mathcal{\theta}}(x(\mathbf{s};\mathbf{t})),
\end{equation}

where \(\theta \in \Theta \subseteq \mathbb{R}^{d_{\theta}}\) is the
associated parameters in the process and \(d_{\theta}\) is the number of
parameter of \(\theta\). An example of spatial processing is to align
variables collected in different resolutions. When variables are
collected at different resolutions, analysts may choose to down-sample
those in a finer resolution, \(i\), to match those in a coarser
resolution, \(i^\prime\). This is a spatial aggregation and if aggregate
using the mean, it can be written as

\begin{equation}
g(x) = \frac{\sum_{i \in i^\prime}x}{n_{i^\prime}},
\end{equation}

where \(i \in i^\prime\) includes all the cells from the finer
resolution in the coarser grid and \(n_{i^\prime}\) is the number of
observations falls into the coarser grid. Other examples of spatial
processing include 1) borrowing information from neighbouring spatial
locations to interpolate unobserved locations and 2) fusing variables
from ground measures with satellite imageries.
